The Next Generation of Canadian Salmon

### 2024-04-19 output/paper.qmd
add model math

@@

>>>>

$$
\begin{aligned}
&\mbox{salmon-population}_i|\mu_i, \sigma \sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \beta_0 +\beta_1\mbox{vessel-count}_i +\beta_2\mbox{boat-days}_i \\
& +\beta_3\mbox{salmon-kept}_i +\beta_4\mbox{salmon-released}_i\\
& +\beta_5\mbox{percentage-gill-net}_i +\beta_6\mbox{percentage-seine}_i\\
& +\beta_7\mbox{percentage-troll}_i\\
\beta_{0, 1, ... 7} &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1) \\
\end{aligned}
$$

@@

$$
\begin{aligned}
&\mbox{next-year-salmon-population}_i|\mu_i, \sigma \sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \beta_0 +\beta_1\mbox{adult-broodstock-removals}_i +\beta_2\mbox{jack-broodstock-removals}_i \\
& +\beta_3\mbox{total-broodstock-removals}_i +\beta_4\mbox{other-removals}_i\\
& +\beta_5\mbox{total-return-to-river}_i \\
\beta_{0, 1, ... 5} &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1) \\
\end{aligned}
$$
